### 2020-04-24 manuscript.rmd
Resize figures.

In 2013, the Centers for Disease Control and Prevention (CDC)'s National Healthcare Safety Network (NHSN) implemented a new surveillance paradigm for adverse ventilator-associated events (VAE), which advanced a broader, objective definition of ventilator-associated complications (VAC) [@Klompas2013-tj; @Magill2013-kw; @Magill2014-xi]. VAC are now defined as an increase of daily minimum positive end-expiratory pressure (PEEP) of at least 3cm H2O or an increase in daily minimum fraction of inspired oxygen (FiO2) by at least 20%, after at least two calendar days of stable or decreasing requirements. There are three tiers of VAC: (1) VAC without signs of infection; infection-associated VAC (IVAC), which are accompanied by leukocytosis/leukopenia or fever/hypothermia, as well as altered antibiotic treatment; and (3) possible ventilator-associated pneumonia (PVAP), which are IVAC with sputum studies suggestive of VA-LRTI. The NHSN definitions of VAE are well validated to predict ventilator-associated morbidity and mortality [@Kobayashi2017-ue; @Meagher2019-py]. VAE criteria also form the basis for promising novel antimicrobial stewardship strategies [@Klompas2017-bw].

However, current VAE surveillance definitions of VAE capture a different population than clinically defined VA-LRTI, which are typically diagnosed by physical examination and radiographic findings, as well as microbiologic test results [@Fan2016-np; @Klompas2014-uv; @Ramirez-Estrada2018-bf; @Stevens2014-zg]. More than 50% of traditionally-defined VA-LRTI fail to meet VAE criteria [@Klompas2019-tt]. The best validated interventions to reduce VAE involve minimizing sedation and careful monitoring of volume status, rather than interventions specifically targeted to infection prevention [@Cocoros2016-md; @Lewis2014-of; @Klompas2015-nj; @Klompas2015-lh; @Rello2019-jl; @Liu2019-fm; @Vaewpanich2019-dr].

Sputum production is a physical examination finding that is often used in the clinical adjudication of VA-LRTI, but its relationship to VAE defined by CDC NHSN criteria is unknown. It is challenging to quantify sputum production, but a marker of sputum production is the frequency with which subglottic suction is performed. Subglottic suction is a procedure performed on an as-needed basis by nurses, respiratory therapists, and physicians to clear lower airway secretions [@Caroff2016-ef]. We sought to evaluate the relationship between the quantity of sputum produced and VAE. Specifically, we sought to define how sputum quantity at the time of VAE relates to sputum quantity before VAE, and to define whether sputum quantity discriminates between VAC and IVAC/VAP, using the frequency of subglottic suction events as a measure of sputum quantity. Here we report the results of a case-crossover study designed to address these questions.

@@

![](figs/main/p_binomial_combined.png){width=750px, align='center'}

@@

![](figs/main/p_ivac_yn_combined.png){width=750px, align='center'}

@@

![](figs/supplement/weibull_survival_vae_vs_admit_ss.png){width=250px, align='center'}

@@

![](figs/supplement/p_ivac_vs_vac_explore.png){width=750px, align='center'}

@@

![](figs/supplement/p_culture_ss_fever.png){width=750px, align='center'}

>>>>

In 2013, the Centers for Disease Control and Prevention (CDC)'s National Healthcare Safety Network (NHSN) implemented a new surveillance strategy for adverse ventilator-associated events (VAE), which advanced a broader, objective definition of ventilator-associated complications (VAC) [@Klompas2013-tj; @Magill2013-kw; @Magill2014-xi]. VAC are now defined as an increase of daily minimum positive end-expiratory pressure (PEEP) of at least 3cm H2O or an increase in daily minimum fraction of inspired oxygen (FiO2) by at least 20%, after at least two calendar days of stable or decreasing requirements. There are three tiers of VAC: (1) VAC without signs of infection; infection-associated VAC (IVAC), which are accompanied by leukocytosis/leukopenia or fever/hypothermia, as well as altered antibiotic treatment; and (3) possible ventilator-associated pneumonia (PVAP), which are IVAC with sputum studies suggestive of VA-LRTI. The NHSN definitions of VAE are well validated to predict ventilator-associated morbidity and mortality [@Kobayashi2017-ue; @Meagher2019-py]. VAE criteria also form the basis for promising, novel antimicrobial stewardship strategies [@Klompas2017-bw].

However, current VAE surveillance definitions of VAE capture a different population than clinically defined VA-LRTI, which are typically diagnosed by physical examination, laboratory test results, and radiographic findings, as well as microbiologic test results [@Fan2016-np; @Klompas2014-uv; @Ramirez-Estrada2018-bf; @Stevens2014-zg]. More than 50% of VA-LRTI defined by clinical, laboratory, and radiographic findings fail to meet VAE criteria [@Klompas2019-tt]. The best validated interventions to reduce VAE involve minimizing sedation and careful monitoring of volume status, rather than interventions specifically targeted to infection prevention [@Cocoros2016-md; @Lewis2014-of; @Klompas2015-nj; @Klompas2015-lh; @Rello2019-jl; @Liu2019-fm; @Vaewpanich2019-dr].

Sputum production is a physical examination finding that is often used in the clinical diagnosis of VA-LRTI, but its relationship to VAE defined by CDC NHSN criteria is unknown. It is challenging to quantify sputum production, but a marker of sputum production is the frequency with which subglottic suction is performed. Subglottic suction is a procedure performed on an as-needed basis by nurses, respiratory therapists, and physicians to clear lower airway secretions [@Caroff2016-ef]. We sought to evaluate the relationship between the quantity of sputum produced and VAE. Specifically, we sought to define how sputum quantity at the time of VAE relates to sputum quantity before VAE, and to define whether sputum quantity discriminates between VAC and IVAC/VAP, using the frequency of subglottic suction events as a measure of sputum quantity. Here we report the results of a case-crossover study designed to address these questions.

@@

```{r fig1, eval=TRUE, autodep=TRUE, fig.align='center', out.width='90%'}

# ![](figs/main/p_binomial_combined.svg){align='center'}  
knitr::include_graphics(path = "./figs/main/p_binomial_combined.svg")

@@

```{r fig2, eval=TRUE, autodep=TRUE, fig.align='center', out.width='90%'}

# ![](figs/main/p_ivac_yn_combined.svg){align='center'}  
knitr::include_graphics(path = "./figs/main/p_ivac_yn_combined.svg")

@@

```{r sfig1, eval=TRUE, autodep=TRUE, fig.align='center', out.width='50%'}

# ![](figs/supplement/weibull_survival_vae_vs_admit_ss.svg){align='center'}  
knitr::include_graphics(path = "./figs/supplement/weibull_survival_vae_vs_admit_ss.svg")

@@

```{r sfig2, eval=TRUE, autodep=TRUE, fig.align='center', out.width='90%'}

# ![](figs/supplement/p_ivac_vs_vac_explore.svg){align='center'}  
knitr::include_graphics(path = "./figs/supplement/p_ivac_vs_vac_explore.svg")

@@

```{r sfig3, eval=TRUE, autodep=TRUE, fig.align='center', out.width='70%'}

# ![](figs/supplement/p_culture_ss_fever.svg){align='center'}  
knitr::include_graphics(path = "./figs/supplement/p_culture_ss_fever.svg")
